\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Joshua}{Ali}{Software engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
18 Elliston St
Chester Hill, NSW 2162
Australia
~
{\Large\faMobilePhone}~+61 416360982
~
\href{mailto:ali.joshua@gmail.com}{{\faEnvelope}~ali.joshua@gmail.com}
\href{https://www.linkedin.com/in/joshuaali}{{\faLinkedinSign}~joshuaali}
\section{Programming}
Java
Javascript
Python
PHP
HTML \& CSS
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{2008--2012}
{Bachelor {\normalfont of Science}}
{The University of New South Wales}
{Specialization in Computer Science}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Full-time}

\begin{entrylist}

%------------------------------------------------

\entry
{2012--now}
{Atlassian}
{}
{\emph{Software developer}
\begin{itemize}
\item Developed an internal staff directory that shows a profile of other staff members and their location on an interactive map. Written in Python and Javascript.
\item Contributed to the development of JIRA, a large Java web application.
\item Contributed to the development of administrator tools for Atlassian Cloud, Atlassian's SaaS platform. Written in Java and Javascript.
\item Contributed to the development of HipChat. Written in Python and PHP.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

\subsection{Internship}

\begin{entrylist}

%------------------------------------------------

\entry
{2011--2012}
{Google}
{}
{\emph{Software engineer intern}
\begin{itemize}
\item Developed a feature for Google Drive's Android app that wraps Java objects and exposes it to Javascript code via JNI and V8's C++ API.
\item Created a code generator using Java and Freemarker to automatically produce the code for the above feature based on Javascript models.
\end{itemize}}

%------------------------------------------------

\entry
{2011}
{Ebix Australia}
{}
{\emph{Web developer intern}
\begin{itemize}
\item Contributed to the development of a Java web application built with the Struts framework.
\end{itemize}}

%------------------------------------------------

\entry
{2010}
{NSW Roads and Traffic Authority}
{}
{\emph{Web developer intern}
\begin{itemize}
\item Enhanced existing JavaServer Faces application to take input via email.
\item Developed Java plug-in for third-party application to synchronize with an LDAP directory.
\item Rewrote Java applet-based website using Javascript.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

\subsection{Part-time}

\begin{entrylist}

%------------------------------------------------

\entry
{2010}
{The University of New South Wales}
{}
{\emph{Tutor} \\
Taught C and VBA.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2008--2012}
{Co-op scholarship}
{The University of New South Wales}
{Program that provided relevant industry training.}

%------------------------------------------------

\end{entrylist}

\end{document}
